Peer single blind review of "Control loops in automotive systems" paper

### 2019-01-10 papers/paper reviews (for ethics course)/rec_2.tex
Added blind paper reviews.

\title{Peer single blind review of "Web-Controlled Robot Based on Raspberry Pi" paper}

@@

The tool which was used: www.copyleaks.com. Results:

    \item 23\% percent of content is similar to other sources
    \item 519 words copied
    \item less than 1 \% minor changes
    \item less than 1 \% of words with related meanings

\section{Abstract and introduction}

    \item Provide a short description of the proposed improvement (solution) in the abstract so that subsequent sections are easier to understand within a context
    \item Expand the solution in the description instead of the lenghty Raspberry PI history

@@

    \item Add reference for "Getting Started" documentation of PiCamera Python library
    \item On Section II "Related work" describe the actual work done to connect the PiCamera to a Raspberry and how its Python library was used to interface with it
    \item Describe the novelty which the proposed solution brings besides interconneting various Raspberry compatible kits with a Raspberry computer.
    \item Provide actual data of how the research went during the control of the robot (communication round trip time, lag, time needed for IP registration, connection loss mitigation, bandwith benchmarks, resolution fallback on low bandwith, etc.)

@@

    \item Provide data interpretation of the tests run on the robot and its connectivity platform
    \item Provide and document the novelty of the proposed solution, together with its significance

@@

Fundamental changes are required for this paper, therefore the paper is rejected.

>>>>

\title{Peer single blind review of "Control loops in automotive systems" paper}

@@

The tool which was used: www.quetext.com Results: no plagiarism detected.

@@

    \item State clearly the novelty of the control loops used
    \item State clearly the novelty of some of the tools and techniques used for verifying the control loops: Unity, UDP, unit tests, systems testing.

@@

    \item Provide data interpretation of the control loop results, using their time diagrams
    \item Discuss the performance of each control loop
    \item Add and briefly discuss future improvements which can be made to this system

@@

Minor revisions are required for this paper.
